\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-12-01 papers/jss/article.Rnw
Make the dotted y=x line in figure 2 dashed with a bigger width to make it more visible.  Suggested by Steve Scott.  Also add some commented out code to add line numbers to make review copies for folks that have offered to do a final review before our resubmit.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@922 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

@@

\begin{figure}[t!]
\begin{center}
<<echo=FALSE,fig=TRUE,width=8,height=4>>=
plot(clean.df$savings.serialized, clean.df$savings.rprotobuf, pch=1, col="red", las=1, xlab="Serialization Space Savings", ylab="Protocol Buffer Space Savings")
points(clean.df$savings.serialized.gz, clean.df$savings.rprotobuf.gz,pch=2, col="blue")
# grey dotted diagonal
abline(a=0,b=1, col="grey",lty=3)

@@

% latex table generated in R 3.0.2 by xtable 1.7-0 package
% Wed Nov 26 15:31:30 2014
%\begin{table}[ht]
%\begin{center}
\begin{tabular}{rlrrrrr}
  \toprule
  Data Set & object.size & \multicolumn{2}{c}{\proglang{R} Serialization} &
  \multicolumn{2}{c}{RProtoBuf Serialization} \\
  & & default & gzipped & default & gzipped \\
  \cmidrule(r){2-6}
 crimtab & 7,936 & 4,641 (41.5\%) & 713 (91.0\%) & 1,655 (79.2\%) & 576 (92.7\%)\\
 faithful & 5,136 & 4,543 (11.5\%) & 1,339 (73.9\%) & 4,936 (3.9\%) & 1,776 (65.5\%)\\
   \hline
 All & 605,256 & 461,667 (24\%) & 138,937 (77\%) & 435,360 (28\%) & 142,134 (77\%)\\
\hline
\end{tabular}
\end{center}
\caption{(Top) Relative space savings of Protocol Buffers and native \proglang{R} serialization over the raw object sizes of each of the \Sexpr{n} data sets in the \pkg{datasets} package. Points to the left of the dotted $y=x$ line represent datasets that are more efficiently encoded with Protocol Buffers. (Bottom) Absolute space savings of two outlier datasets and the aggregate performance of all datasets.}
\label{fig:compression}
\end{figure}

>>>>

% Line numbers for drafts.
%\usepackage[switch, modulo]{lineno}
%\linenumbers

@@

\begin{figure}[t!]
\begin{center}
<<echo=FALSE,fig=TRUE,width=8,height=4>>=
plot(clean.df$savings.serialized, clean.df$savings.rprotobuf, pch=1, col="red", las=1, xlab="Serialization Space Savings", ylab="Protocol Buffer Space Savings")
points(clean.df$savings.serialized.gz, clean.df$savings.rprotobuf.gz,pch=2, col="blue")
# grey dotted diagonal
abline(a=0,b=1, col="grey",lty=2,lwd=3)

@@

% latex table generated in R 3.0.2 by xtable 1.7-0 package
% Wed Nov 26 15:31:30 2014
%\begin{table}[ht]
%\begin{center}
\begin{tabular}{rlrrrrr}
  \toprule
  Data Set & object.size & \multicolumn{2}{c}{\proglang{R} Serialization} &
  \multicolumn{2}{c}{RProtoBuf Serialization} \\
  & & default & gzipped & default & gzipped \\
  \cmidrule(r){2-6}
 crimtab & 7,936 & 4,641 (41.5\%) & 713 (91.0\%) & 1,655 (79.2\%) & 576 (92.7\%)\\
 faithful & 5,136 & 4,543 (11.5\%) & 1,339 (73.9\%) & 4,936 (3.9\%) & 1,776 (65.5\%)\\
   \hline
 All & 605,256 & 461,667 (24\%) & 138,937 (77\%) & 435,360 (28\%) & 142,134 (77\%)\\
\hline
\end{tabular}
\end{center}
\caption{(Top) Relative space savings of Protocol Buffers and native \proglang{R} serialization over the raw object sizes of each of the \Sexpr{n} data sets in the \pkg{datasets} package. Points to the left of the dashed $y=x$ line represent datasets that are more efficiently encoded with Protocol Buffers. (Bottom) Absolute space savings of two outlier datasets and the aggregate performance of all datasets.}
\label{fig:compression}
\end{figure}
